---
title: "Titanic"
author: "Ankit Ranjan"
---

### Preparation

Set seeds to make this code repeatable, import all necessary packages
```{r set seed}
library(caret)
library(randomForest)
library(fields)
library(e1071)
set.seed(42)
```

### Set Working Directory and Load Data
```{r }
setwd('D:/Kaggle/Titanic')
trainSet <- read.table("train.csv", sep = ",", header = TRUE)
testSet <- read.table("test.csv", sep = ",", header = TRUE)
```

### Doing initial analysis on the features
```{r}
table(trainSet[,c("Survived", "Pclass")])
table(trainSet$Survived,trainSet$SibSp)
table(trainSet$Survived,trainSet$Parch)
bplot.xy(trainSet$Survived, trainSet$Age)
bplot.xy(trainSet$Survived, trainSet$Fare)
```

### Train Model

First we set Survived as a factor and then do the modelling.

```{r }
trainSet$Survived <- factor(trainSet$Survived)
model <- train(Survived ~ Pclass + Sex + SibSp + Embarked + Parch + Fare,data = trainSet,method = "rf",trControl = trainControl(method = "cv",number = 5))
#model summary
model
```

### Determine the values for Test set
The initial prediction gave error. Upon checking i realised the Fare for one of the rows has N/A value. So, the values was replaced by the mean of overall fares.
```{r }
testSet$Fare <- ifelse(is.na(testSet$Fare), mean(testSet$Fare, na.rm = TRUE), testSet$Fare)
testSet$Survived <- predict(model, newdata = testSet)
```

### Submit Data !